The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-09 paper/ms.tex
hump and spike stars

>>>>

\subsection{Classical Pulsators}

Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{th}$-brightest stars on silicon and the brightest two stars that show this effect. \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes. The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence. With an absolute $G$~mag of 1.402, it is significantly fainter than the bright B3e star HD~183362 at $G = -2.576$.
